---
title: "Calculating Matching Coverage"
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE}
sector_in_scope <- glue::glue_collapse(
  unique(r2dii.data::ald_demo$sector), sep = ", ", last = ", and "
)
```

`r2dii.match` allows you to match loans from your loanbook to the companies in an asset-level dataset, but it is unlikely that you will be able to match every loan. There are a couple reasons for this. A loan-taking company may not be active in the sectors 2DII focuses on: `r sector_in_scope`; and even if the company does operate within 2DII's scope, the asset-level dataset may lack information about it. 

How can you measure how much of the loanbook matched some asset? This article shows two ways to calculate such matching coverage: (1) Calculate the portion of your loanbook covered, by dollar value (i.e. using one of the `loan_size_*` columns); and (2) Count the number of companies matched.

### Setup

First we will need to load up the useful packages:

```{r}
library(dplyr, warn.conflicts = FALSE)
library(purrr)
library(ggplot2)
library(r2dii.data)
library(r2dii.match)
```

We will use example datasets from `r2dii.data`. To demonstrate our point, we create a `loanbook` dataset with two mismatching loans:

```{r}
loanbook <- loanbook_demo %>% 
  mutate(
    name_ultimate_parent = 
      ifelse(id_loan == "L1", "unmatched company name", name_ultimate_parent),
    sector_classification_direct_loantaker = 
      ifelse(id_loan == "L2", 99, sector_classification_direct_loantaker)
  )
```

We will then run the matching algorithm on this loanbook:

```{r}
matched <- loanbook %>% 
    match_name(ald_demo) %>% 
    prioritize()
```

Note that this `matched` dataset will contain _only_ loans that were matched successfully. To determine coverage, we need to go back to the original `loanbook` dataset. We must determine the 2DII sectors of each loan, as dictated by the `sector_classification_direct_loantaker` column. 

For this, we join the loanbook with the [`sector_classifications`](https://2degreesinvesting.github.io/r2dii.data/reference/sector_classifications.html) dataset, which lists all sector classification code standards used by 'PACTA'. Unfortunately we need to work around two caveats (you may ignore them because they are conceptually uninteresting):

* In the two datasets, the columns we want to merge by have different names. We use the argument `by` to `left_join()` to merge the columns `sector_classification_system` and `sector_classification_direct_loantaker` (from `loanbook`) with the columns `code_system` and `code` (from `sector_classifications`), respectively. 

* In the two datasets, the sector classification codes are represented with different data-types. We modify the column `sector_classification_direct_loantaker` before `left_join()` so it has the same type as the corresponding column `code` (otherwise `left_join()` throws an error), and again after `left_join()` to restore its original type. 

```{r}
merge_by <- c("code_system", "code") %>% 
  set_names(paste0("sector_classification_", c("system", "direct_loantaker")))

loanbook_with_sectors <- loanbook %>% 
  modify_at(names(merge_by)[[2]], as.character) %>% 
  left_join(sector_classifications, by = merge_by) %>% 
  modify_at(names(merge_by)[[2]], as.double)
```

We can join these two datasets together, to generate our `coverage` dataset:

``` {r}
coverage <- left_join(loanbook_with_sectors, matched) %>% 
  mutate(
    loan_size_outstanding = as.numeric(loan_size_outstanding),
    loan_size_credit_limit = as.numeric(loan_size_credit_limit),
    matched = case_when(
      score == 1   ~ "Matched", 
      is.na(score) ~ "Not Matched",
      TRUE         ~ "Not Mached"
    ),
    sector = case_when(
      borderline == TRUE & matched == "Not Matched" ~ "not in scope",
      TRUE ~ sector
    )
  )
```

### 1. Calculate the portion of your loanbook covered by dollar value

From the `coverage` dataset, we can calculate the total loanbook coverage by dollar value. Let's create two helper functions, one to calculate dollar-value and another one to plot coverage in general.

```{r}
dollar_value <- function(data, ...) {
  data %>% 
    group_by(matched, ...) %>% 
    summarize(loan_size_outstanding = sum(loan_size_outstanding))
}

plot_coverage <- function(data, x, y) {
  ggplot(data) + 
    geom_col(aes({{x}}, {{y}}, fill = matched)) +
    # Use more horizontal space -- avoids overlap on x axis text
    theme(legend.position = "top")
}
```

Let's first explore all loans.

```{r}
coverage %>% 
  dollar_value() %>% 
  plot_coverage(matched, loan_size_outstanding)
```

To calculate the total, in-scope, loanbook coverage: 

```{r}
coverage %>% 
  filter(sector != "not in scope") %>% 
  dollar_value() %>% 
  plot_coverage(matched, loan_size_outstanding)
```

### Break down by sector

You may break-down the plot by sector: 

```{r}
coverage %>% 
  dollar_value(sector) %>% 
  plot_coverage(sector, loan_size_outstanding)
```

Or even further, by matching level:

```{r}
coverage %>% 
  mutate(matched = case_when(
    matched == "Matched" & level == "direct_loantaker"      ~ "Matched DL",
    matched == "Matched" & level == "intermediate_parent_1" ~ "Matched IP1",
    matched == "Matched" & level == "ultimate_parent"       ~ "Matched UP",
    matched == "Not Matched"                                ~ "Not Matched",
    TRUE                                                    ~ "Catch unknown"
  )) %>% 
  dollar_value(sector) %>% 
  plot_coverage(sector, loan_size_outstanding)
```

### 2. Count the number of companies

You might also be interested in knowing how many companies in your loanbook were 
matched. It probably makes most sense to do this at the `direct_loantaker` 
level:

``` {r}
companies_matched <- coverage %>% 
  group_by(sector, matched) %>% 
  summarize(no_companies = n_distinct(name_direct_loantaker))

companies_matched %>% 
  plot_coverage(sector, no_companies)
```

## A Note on Sector Classifications and the `borderline` Flag

There are a zoo of sector classification code systems out there. Some are 
granular, some are not. Since we currently cover a particular portion of the 
supply chain (i.e. production), it is important we try to only match 
the ALD with companies that are actually active in this portion of the supply 
chain. 

An issue arises when, for example, a company is classified in the "power 
transmission" sector. In a perfect world, these companies would produce no 
electricity, and we would not try to match them. In practice, however, we find 
there is often overlap. For this reason, we introduced the `borderline` flag.

In the example below, we see two classification codes coming from the SIC 
classification standard:

``` {r}
r2dii.data::sic_classification %>% 
  filter(code %in% c(41111, 36200))
```

Notice that the code 41111 corresponds to power generation. This is an identical 
match to 2DII's `power` sector, and thus the `borderline` flag is set to 
`FALSE`. In contrast, code 36200 corresponds to the manufacture of electricity 
distribution and control apparatus. In a perfect world, we would set this code 
to `not in scope`, however there is still a chance that these companies produce 
electricity. For this reason, we have mapped it to `power` with 
`borderline = TRUE`.

In practice, if a company has a `borderline` of `TRUE` and IS matched, then 
consider the company in scope. If it has a `borderline` of `TRUE` and ISN'T 
matched, then consider it out of scope.
