---
title: "r2dii.match 0.0.1"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

We're happy to announce that r2dii.match is now on CRAN. 

r2dii.match matches data from financial portfolios to asset level data from
market-intelligence databases (e.g. power plant capacities, emission factors,
etc.). This is the first step to assess if a financial portfolio aligns with
climate goals. For details see the package's 
[website](https://2degreesinvesting.github.io/r2dii.match/) and
<https://2degrees-investing.org/>.

Install r2dii.match with:

```r
install.packages("r2dii.match")
```

And use it with:

```{r setup}
library(r2dii.match)
```

[`match_name()`](https://2degreesinvesting.github.io/r2dii.match/reference/match_name.html) matches a loanbook and asset-level dataset (ald). Let's try it with [demo datasets from the package r2dii.data](https://2degreesinvesting.github.io/r2dii.data/reference/index.html).

```{r}
# install.packages("r2dii.data")
library(r2dii.data)

loanbook_demo
ald_demo

matched <- match_name(loanbook_demo, ald_demo)
matched
```

Next you should validate the matched data ([learn how](https://2degreesinvesting.github.io/r2dii.match/articles/r2dii-match.html)).

Finally, [`prioritize()`](https://2degreesinvesting.github.io/r2dii.match/reference/prioritize.html) takes matched data and picks rows of highest priority.

```{r}
prioritize(matched)
```

We look forward to [your feedback](https://github.com/2DegreesInvesting/r2dii.match/issues).

## Acknowledgements

```{r echo=FALSE}
thank <- function(x) {
  x <- sort(x)
  paste0("[", x, "]", sprintf("(https://github.com/%s)", x), collapse = ", ")
}

contributors <- c(
  "Clare2D",
  "cjyetman",
  "georgeharris2deg",
  "koopmand",
  "vintented"
)
```

A big thanks to all `r length(contributors)` contributors who helped with ideas, code, or reviews: `r thank(contributors)`.
